Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Refines slide formatting and updates code examples
- Adjusts slide 17 text layout for better readability.
- Updates code example on slide 18.
- Addresses formatting inconsistencies.

## From Framework to Workflow: Introducing {bidux} {.center background-color="#e6f0ff"}

:::: {.columns}
::: {.column width="48%"}

- **Current Features (Phase 1):**
  * 📚 Concept browser
    * `bid_concept("processing fluency")`
  * 🧠 BID stage functions
    * `bid_notice()` to `bid_validate()`
:::

::: {.column width="48%"}

- **Coming Soon (Phases 2-4):**
  * 🤖 LLM Integration 
  * 🛠️ UI Component Library
  * 📊 Testing and Validation Tools
:::
::::

@@

- "We're not just sharing a framework - we're building tools to make it easy to adopt"
- "We're excited to introduce `{bidux}`...our new R package currently in **Phase 1 development** that helps implement the BID framework with your workflows"
- "Our goal is to make these psychological principles accessible to every R developer"
- Current features focus on documentation and knowledge
- Future features will include ready-to-use UI components with BID principles built in
- "The LLM integration will let you describe what you want in plain language"
- "Think of {bidux} as your behavioral science assistant for dashboard development"
- "This is in active development - and not quite stable yet, but please stay tuned"
:::

@@

# 1. Concept dictionary functionality
processing_fluency <- bid_concept("Processing Fluency")
print(processing_fluency)

# 2. Stage documentation (piped workflow)
project_docs <- bid_notice(
  problem = "Dashboard overload", 
  theory = "Cognitive Load Theory",
  evidence = "User testing results"
) |>
  bid_interpret(
    central_question = "How to simplify?",
    data_story = list(hook = "Too complex", context = "Many tabs")
  )
print(project_docs)
```

@@

- "The concept dictionary gives you instant access to behavioral principles"
- "Each concept includes definition, code examples, and empirical evidence"
- "The stage documentation functions help structure your design thinking"
- "These functions integrate with dplyr workflows via pipes"
- "Documentation becomes part of your development process, not separate"
- Point out the commented future code to generate excitement
- "In Phase 2, you'll be able to ..."
- When the link appears: "We're launching this at ShinyConf today - check out the repo"
:::

@@

::: {.nonincremental}
1. **BID** helps reduce friction and improve decisions
2. **`{reactable}` + `{echarts4r}`** help bring BID to life
3. **`{bidux}`** supports you in applying BID at every stage (try it today!)
4. Build dashboards that guide — not fry — your users
:::

>>>>

## From Framework to Workflow: {bidux} {.center background-color="#e6f0ff"}

:::: {.columns .r-fit-text}

::: {.column width="56%" .nonincremental .fragment}
- **Current Features (Phase 1):**
  * 📚 Concept browser
    * `bid_concept("processing fluency")`
  * 🧠 BID stage functions
    * `bid_notice()` to `bid_validate()`
:::

::: {.column width="42%" .nonincremental .fragment}
- **Coming Soon (Phases 2-4):**
  * 🤖 LLM Integration 
  * 🛠️ UI Component Library
  * 📊 Testing and Validation Tools
:::

@@

- "We're not just sharing a framework - we're building tools to make it easy to adopt"
- "We're excited to introduce `{bidux}`...our new R package currently in **Phase 1 development** that helps implement the BID framework with your workflows"
- "Our goal is to make these psychological principles accessible to every R developer"
- Current features focus on documentation and knowledge
- Future features will include ready-to-use UI components with BID principles built in
- "The LLM integration will let you describe what you want in plain language"
- "Think of {bidux} as your behavioral science assistant for Shiny app development"
:::

@@

# concept dictionary functionality
processing_fluency <- bid_concept("processing fluency")
print(processing_fluency)

# BID stage documentation functionality (piped workflow)
project_docs <- bid_notice(
  problem = "users overwhelmed by filtering options", 
  theory = "cognitive load theory", # use if wanting to apply specific concept; leave blank if unsure
  evidence = c("user feedback results", "dashboard telemetry data")
) |>
  bid_interpret(
    central_question = "How to simplify?",
    data_story = list(hook = "Too complex", context = "Many tabs")
  )
print(project_docs)
```

@@

- "The concept dictionary gives you instant access to behavioral principles"
  * "Each concept includes definition, code examples, and empirical evidence"
- "The stage documentation functions help structure your design thinking"
  * "These functions are designed to work together via pipes (cf, tidyverse)"
- "Documentation becomes part of your development process, not separate"
- Point out the commented future code to generate excitement
- "In Phase 2, you'll be able to ..."
- When the link appears: "We're launching this at ShinyConf today - check out the repo"
:::

@@

::: {.nonincremental}
1. **BID** helps reduce friction and improve decisions
2. **`{reactable}` + `{echarts4r}`** help bring BID to life
3. **`{bidux}`** supports you in applying BID at every stage<br>(try it today!)
4. Build dashboards that guide — not fry — your users
:::
